\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvparagraph}

  \hlim{Poslih the below by yourself! + Convince the other person WHY you want to gain experience in academia after working in industry here.}
A semiconductor researcher focused on interconnect metallization and advanced process technologies 
that are essential for next-generation semiconductor scaling.  
Studying new materials and process innovations to enable reliable interconnect scaling 
and to improve overall chip performance.  
An advocate of collaborative research, aiming to accelerate semiconductor technology advancement 
and contribute to the global microelectronics community.  
Currently, a researcher at the \href{https://www.samsungfoundry.com}{Samsung Electronics Foundry}, Republic of Korea.  
Previously contributed as a process engineer and R\&D specialist in cross-disciplinary teams, 
leading projects that bridged materials science, process integration, and large-scale manufacturing.  
\end{cvparagraph}

\newcommand{\lineintv}{\vspace{0.0cm}} % Not in use

\cventry
  {} % Degree
  {Highlights\vspace{-0.3cm}\hlim{Highlight the expertise you developed at the company.}} % Institution
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems} % Description(s) bullet points
      \item {Over 6 years of research and development experience in interconnect process technologies at Samsung Electronics Foundry}
      \item {Led projects on scaling down interconnect metals through novel materials and advanced fabrication methods}
      \item {Improved semiconductor device performance and reliability by optimizing metallization processes}
      \item {Collaborated with multidisciplinary teams across materials science, device physics, and process engineering}
      \item {Contributed to high-volume manufacturing readiness for advanced process nodes}
    \end{cvitems}
  }

 \cventry
  {My research interests include, but are not confined to:} % Degree
  {Field of Interest}%\vspace{-0.3cm}} % Institution
  {} % Location
  {} % Date(s)
  {
  % NOTE(hlim): might be better to use other enumeration for other professors who have different research fields
    \begin{cvitems} % Description(s) bullet points
      \item {Interconnect metallization and scaling for advanced semiconductor nodes\lineintv}
      \item {Materials engineering for barrier/liner and low-resistivity metals\lineintv}
      \item {Process development for yield and reliability improvement\lineintv}
      \item {Integration of new metallization processes into high-volume manufacturing\lineintv}
      \item {Electrical performance enhancement through optimized interconnect design\lineintv}
      \item {Semiconductor device scaling and manufacturability\lineintv}
    \end{cvitems}
  }

