%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Samsung Electronics, Foundry} % Job title
    {SF2 Logic device, M1 24P Task Force} % Organization
    {S.Korea} % Location
    {Jun. 2025 - Sep. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved 2nm logic device yield through 24P (13 nm width, 11 nm space) BEOL(Back-End-of-line) process scheme optimization}
        \item {Developed SESL(Single Etch stopped layer) scheme in 2nm logic device}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Samsung Electronics, Foundry} % Job title
    {SF2 Logic device, BEOL Process Architecture} % Organization
    {S.Korea} % Location
    {Jun. 2023 - May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed SF2 (Samsung Foundry 2nm) Logic device BEOL interconnect part}
        \item {Enhanced SF2 logic device performance using CuMn and a thin Co liner}
        \item {Enhanced SF2 Logic Device performance with High density Low-k material in interconnection}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Samsung Electronics, Semiconductor R\&D Center/Foundry} % Job title
    {SF3 Logic device, BEOL Process Architecture} % Organization
    {S.Korea} % Location
    {Mar. 2021 - MAY. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Replaced ALD barrier metal with reverse-selected barrier metal, reducing resistance and enhancing device performance}
        \item {Developed a self-aligned universal patterning process for the first, second, and third narrow-width BEOL metal layers}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Samsung Electronics, Semiconductor R\&D Center} % Job title
    {SF4 Logic device, BEOL Technology development} % Organization
    {S.Korea} % Location
    {Mar. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved SF4 Logic device yield by Litho–Etch–Litho–Etch process combined with cut patterning}
        \item {Enhanced SF4 Logic device performance with ALD Barrier metal process}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {KAIST, Korea Institute of Energy Research (KIER)} % Job title
    {Cu₂ZnSnSe₄ Solar Cell} % Organization
    {Daejwon, S.Korea} % Location
    {Mar. 2018 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of earth‑abundant Cu₂ZnSnSe₄ solar cells on flexible titanium substrate}
        \item {effects of Film Growth Temperatures on Device Performances}
      \end{cvitems}
    }

%---------------------------------------------------------

      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}

%---------------------------------------------------------
\end{cventries}
